Measuring security performance in the Android ecosystem

### 2015-06-08 security_scoring.tex
update captions

\begin{figure*}
 \centering
 \includegraphics[width=0.9\textwidth]{figures/full_version_comp.pdf}
 \caption{Full version distributions for the highest and lowest scoring model}
 \label{fig:full_version_comp}
\end{figure*}

@@

\subsection{Scores over time}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/security_score_manufacturer}
\caption{Security scores for different manufacturers}
\label{fig:security_score_manufacturer}
\includegraphics[width=\columnwidth]{figures/security_score_model}
\caption{Security scores for different device models}
\label{fig:security_score_model}
\includegraphics[width=\columnwidth]{figures/security_score_operator}
\caption{Security scores for different operators}
\label{fig:security_score_operator}
\includegraphics[width=\columnwidth]{figures/security_score_summary}
\caption{Security scores for Nexus and non-Nexus devices\todo{subfig?}\todolater{bridge gaps?}}
\label{fig:security_score_summary}
\end{figure}
\todo{This is method rather than result}
The scoring metric as originally computed is averaged over the whole history of the device manufacturer, device model or network operator, it gives equal weight to periods years ago as to in the last few months.
If instead we take an exponential moving average of the daily score for days with more than \daSigNumDevicesDay\ devices when there have been at least consecutive \daSigNumDays\ days of data with that many devices then we can plot how this score has changed over time.
Equation~\ref{eq:rolling_update} shows how the value for a particular day ($v_i$) is computed from the previous day's value and the input for the current day ($n$) with an $\alpha$ of $1/\daSigNumDays$.
\begin{equation}
v_i = v_{i-1} (1 - \alpha) + n \alpha
\label{eq:rolling_update}
\end{equation}
Figure~\ref{fig:security_score_manufacturer} shows this for manufacturers, Figure~\ref{fig:security_score_model} for device models, Figure~\ref{fig:security_score_operator} for operators Figure~\ref{fig:security_score_summary} for Nexus and non-Nexus devices; these figures are shown with their 95\% confidence intervals.
These show how the scores for different entities are different and change over time, while there is correlated behaviour for different entities (due to things like new vulnerabilities affecting all Android being discovered) these lines still have crossings due to the different behaviour of the different entities.
It also shows that we do not have sufficient data for all the entities all of the time, resulting in gaps in the data.
The clearest results are for Figure~\ref{fig:security_score_summary} with a large gap between the scores for Nexus and non-Nexus devices across the whole data set.

>>>>

\begin{figure*}
 \centering
 \includegraphics[width=0.9\textwidth]{figures/full_version_comp.pdf}
 \caption{Full version distributions for the highest and lowest scoring models}
 \label{fig:full_version_comp}
\end{figure*}

@@

\subsection{Scores over time}
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/security_score_manufacturer}
\caption{Security scores for different manufacturers}
\label{fig:security_score_manufacturer}
\includegraphics[width=\columnwidth]{figures/security_score_model}
\caption{Security scores for different device models}
\label{fig:security_score_model}
\includegraphics[width=\columnwidth]{figures/security_score_operator}
\caption{Security scores for different operators}
\label{fig:security_score_operator}
\includegraphics[width=\columnwidth]{figures/security_score_summary}
\caption{Security scores for Nexus and non-Nexus devices\todolater{bridge gaps?}}
\label{fig:security_score_summary}
\end{figure}
\todo{This is method rather than result}
The scoring metric as originally computed is averaged over the whole history of the device manufacturer, device model or network operator, it gives equal weight to periods years ago as to in the last few months.
If instead we take an exponential moving average of the daily score for days with more than \daSigNumDevicesDay\ devices when there have been at least consecutive \daSigNumDays\ days of data with that many devices then we can plot how this score has changed over time.
Equation~\ref{eq:rolling_update} shows how the value for a particular day ($v_i$) is computed from the previous day's value and the input for the current day ($n$) with an $\alpha$ of $1/\daSigNumDays$.
\begin{equation}
v_i = v_{i-1} (1 - \alpha) + n \alpha
\label{eq:rolling_update}
\end{equation}
Figure~\ref{fig:security_score_manufacturer} shows this for manufacturers, Figure~\ref{fig:security_score_model} for device models, Figure~\ref{fig:security_score_operator} for operators Figure~\ref{fig:security_score_summary} for Nexus and non-Nexus devices; these figures are shown with their 95\% confidence intervals.
These show how the scores for different entities are different and change over time, while there is correlated behaviour for different entities (due to things like new vulnerabilities affecting all Android being discovered) these lines still have crossings due to the different behaviour of the different entities.
It also shows that we do not have sufficient data for all the entities all of the time, resulting in gaps in the data.
The clearest results are for Figure~\ref{fig:security_score_summary} with a large gap between the scores for Nexus and non-Nexus devices across the whole data set.
